Notes for General Relativity

### 2016-09-25 Complex Geometry - index/misc/complex geometry-misc.tex
Daily update.

@@

    Facts he mentioned that I am not familiar
    \begin{enumerate}
        \item $Gl(2,\mathbb{C})$ is diffeomorphic to $U(2)\times\mathbb{R}^4$.
        \item $Gl^+(4,\mathbb{R})$ is diffeomoprhic to $SO(4)\times
            \mathbb{R}^10$
        \item In the usual inclusion $Gl(2,\mathbb{C})\rightarrow
            Gl^+(4,\mathbb{R})$, $U(2)$ becomes a subgroup of $SO(4)$.
    \end{enumerate}
    Concepts to be learnt:
    \begin{enumerate}
        \item fibration of above Lie groups
        \item Hightlight area 1: can fibration kill a subgroup?
        \item Hightlight area 2: contractible and fibration?
        \item And the following sentence.
        \item then the next sentence: diffeomoprhism and homotopy?
        \item How does a "chain of subgroups" gives rise to a fibration.
    \end{enumerate}
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
  \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
  \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
  \bibitem{math.se_4} \href{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
  {Similar matrices and field extensions}
  \bibitem{math.se_set-of-almost} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}
\end{thebibliography}
\printnomenclature

>>>>

% For category graphs
\usepackage[all]{xy}

@@

    Facts he mentioned that I am not familiar
    \begin{enumerate}
        \item $Gl(2,\mathbb{C})$ is diffeomorphic to $U(2)\times\mathbb{R}^4$.
        \item $Gl^+(4,\mathbb{R})$ is diffeomoprhic to $SO(4)\times
            \mathbb{R}^10$
        \item In the usual inclusion $Gl(2,\mathbb{C})\rightarrow
            Gl^+(4,\mathbb{R})$, $U(2)$ becomes a subgroup of $SO(4)$.
    \end{enumerate}
    Concepts to be learnt:
    \begin{enumerate}
        \item fibration of above Lie groups
        \item Hightlight area 1: can fibration kill a subgroup?
        \item Hightlight area 2: contractible and fibration?
        \item And the following sentence.
        \item then the next sentence: diffeomoprhism and homotopy?
        \item How does a "chain of subgroups" gives rise to a fibration.
    \end{enumerate}

    The following notes are aim at understanding the above sentences.

    \subsection{Lifting Property}
    \label{sec:Lifting-Property}
    \paragraph{Lift of morphisms}
    \begin{defi}[Lift of morphisms]
    \nomenclature{Lift of morphisms}{\nomrefpage.}
        The \textbf{lift} of a morphism $f: Y\to B$ along an epimorphism
        \footnote{Epimorphism is the category analogy of surjective
        functions in set theory}. (or more general map) $p:X\to B$ is a
        morphism $\tilde{f}: Y\to X$ such that $f = p\circ\tilde{f}$.
    \end{defi}
    $$
    \xymatrix{
        X\ar[r]^p                    & B \\
        Y\ar[ur]^f\ar[u]^{\tilde{f}} & \\
    }
    $$
    \begin{defi}[Lift property]
    \nomenclature{Lift property}{\nomrefpage.}
        We say that $f$ has a \textbf{left lifting property} w.r.t $g$, or
        equivalently that $g$ has a \textbf{right lifting property} w.r.t
        $f$, if and only if for every commutative diagram below:
        $$
        \xymatrix{
        a\ar[r]^u\ar[d]^f & c\ar[d]^g \\
        b\ar[r]^v         & d
        }
        $$
        there is an arrow $\gamma$, s.t. both triangles in the followinng
        diagram commutes.
        $$ \xymatrix{
        a\ar[r]^u\ar[d]^f         & c\ar[d]^g \\
        b\ar[r]^v\ar[ru]^{\gamma} & d
        }$$
        Such an arrow $\gamma$ is called a \textbf{lift} or a 
        \textbf{solution} to the lifting problem $(u,v)$.
        If such $\gamma$ is unique, i.e. we have:
        $$ \xymatrix{
        a\ar[r]^u\ar[d]^f         & c\ar[d]^g \\
        b\ar[r]^v\ar@{.>}[ru]^{\gamma} & d
        }$$
        Then we say $f$ is \textbf{orthogonal} to $g$, denoted $f \perp g$.
    \end{defi}
    ref \cite{nlab-lift}.

    % Resources: https://ncatlab.org/nlab/show/fibration
    %            https://ncatlab.org/nlab/show/homotopy+lifting+property
    %            https://en.wikipedia.org/wiki/Homotopy_lifting_property
    %            https://en.wikipedia.org/wiki/Fibration
\section{Anchor}
\label{sec:Anchor}

\begin{thebibliography}{1}
  \bibitem{book} D Huybrechts's Introduction to Complex Geometry.
  \bibitem{math.se_1} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}.
  \bibitem{math.se_2} \href{http://math.stackexchange.com/questions/1356823/does-gln-mathbbc-inject-into-gl2n-mathbbr-for-all-n}{Does $GL(n,\mathbb{C})$ inject into $GL^+(2n, \mathbb{R})$ for all $n$?}
  \bibitem{determinants_of_block_m} John R. Silvester, 
      Determinants of Block Matrices. Available in WebArchive link:
      \url{https://web.archive.org/web/20140505161153/http://www.mth.kcl.ac.uk/~jrs/gazette/blocks.pdf}
  \bibitem{math.se_3} \href{http://math.stackexchange.com/questions/1927487/making-sense-of-frac-mathrmgl2n-mathbbr-mathrmgln-mathbbc/1927518?noredirect=1#comment3957369_1927518}{Making sense of $\frac{\mathrm{GL}(2n,\mathbb{R})}{\mathrm{GL}(n,\mathbb{C})}$}
  \bibitem{math.se_4} \href{http://math.stackexchange.com/questions/57242/similar-matrices-and-field-extensions?noredirect=1&lq=1}
  {Similar matrices and field extensions}
  \bibitem{math.se_set-of-almost} \href{http://math.stackexchange.com/questions/923957/set-of-almost-complex-structures-on-mathbb-r4-as-two-disjoint-spheres}{set of almost complex structures on $\mathbb{R}^4$ as two disjoint spheres}
  \bibitem{nlab-lift}\href{https://ncatlab.org/nlab/show/lift}{nLab Lift}
\end{thebibliography}
\printnomenclature

### 2016-09-25 Draft/draft.tex
Daily update.

    To resist the flow of current carried by Copper Pair, is equivlant to destroying a pair of Copper Pair:
    $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$

@@

    We have also an extended form. Suppose the event space is partitioned
    into $\{A_i\}$, then we have (also easily proved):
    \begin{align}
        P(A_i|B)=\frac{P(B|A_i)P(A_i)}{\sum_j P(B|A_j)P(A_j)}
    \end{align}
    Here's a good reading \href{http://plato.stanford.edu/entries/bayes-theorem/}{Bayes' Theorem in SEP}.
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} 
        Bosonization and Strongly Correlated Systems. Cambridge.
        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}

>>>>

    To resist the flow of current carried by Copper Pair, is equivalent to destroying a pair of Copper Pair:
    $$ \braket{C_{k \uparrow}C_{-k \downarrow} } \longrightarrow C_{k \uparrow}C_{-k \downarrow}$$

@@

    We have also an extended form. Suppose the event space is partitioned
    into $\{A_i\}$, then we have (also easily proved):
    \begin{align}
        P(A_i|B)=\frac{P(B|A_i)P(A_i)}{\sum_j P(B|A_j)P(A_j)}
    \end{align}
    Here's a good reading \href{http://plato.stanford.edu/entries/bayes-theorem/}{Bayes' Theorem in SEP}.
    \subsection{About Matlab}
    \label{sec:About-Matlab}
    \paragraph{On using $A/B$ or $A\\B$}
    Matlab's matrix divide function \texttt{mrdivide}, \texttt{mldivide}
    , abbrevated $A/B$ and $A\\B$, are different and should be used with
    caution. One can check that:
    \begin{center}
        $A\cdot D^{-1}$ is equivalent to $A/D$, $D^{-1}\cdot A$ is
        equivalent to $D\backslash A$.
    \end{center}
    Also, it is straightforward to prove that the two are equal if and only if $A$ commutes with $D$.
\section{Anchor}
% This is just an anchor for seperating thebibliography from above contents.
\begin{thebibliography}{1}
	\bibitem{Sakurai} Sakurai, J. J. Modern Quantum Mechanics, Addison Wesley.
	\bibitem{BSCS} 
        Bosonization and Strongly Correlated Systems. Cambridge.
        \href{http://www.cambridge.org/us/academic/subjects/physics/condensed-matter-physics-nanoscience-and-mesoscopic-physics/bosonization-and-strongly-correlated-systems}{Cambridge Press Link}

### 2016-09-25 G.R/G.R.tex
Daily update.

    Aided with this formula, Landau discusses the \textit{Lorentz
    contraction} phenomenon in special relativity and defines
    the proper length\nomenclature{proper length}{\nomrefpage}
    $l_0$, defined as the length in its rest frame. It is related
    to its length measured in another frame $K'$ by:
    \begin{align}
        l' = l_0 \sqrt{1-v^2}
    \end{align}

@@

    And:
    \begin{align}
        e^{prst}A_{ip}A_{kr}A_{ls}A_{mt} &= -A e_{iklm} \\
        e^{iklm}e^{prst}A_{ip}A_{kr}A_{ls}A_{mt} &= 24 \;\mathrm{det}(A)
    \end{align}
    Next the autho introduces the dual tensors. Since this is important
    and the case of Lorentzian spacetime is somewhat different from
    the usual case, this topic deserves a separate treatment in the
    following section.

    \subsection{Dual Tensors}
    \label{sec:Dual_Tensors}
    % TODO See this post:http://physics.stackexchange.com/questions/37577/what-does-the-dual-of-a-tensor-mean-e-g-dual-stress-tensor-in-relativistic-ed
    \subsection{Light's life}
    \label{sec:Lights_life}
    The life of a proton must be miserable.

>>>>

    Note that in matrix form, (using the popular notations
    $\tensor[]{\Lambda}{^\nu_\mu},\gamma, \text{and }\beta$):
    \begin{align}
        \tensor[]{\Lambda}{^\nu_\mu} =
        \left( \begin{array}{cccc}
         \gamma        & -\gamma \beta & 0 & 0 \\
         -\gamma \beta & \gamma        & 0 & 0 \\
         0             & 0             & 0 & 0 \\
         0             & 0             & 0 & 0 \\
        \end{array} \right)
    \end{align}
    Aided with this formula, Landau discusses the \textit{Lorentz
    contraction} phenomenon in special relativity and defines
    the proper length\nomenclature{proper length}{\nomrefpage}
    $l_0$, defined as the length in its rest frame. It is related
    to its length measured in another frame $K'$ by:
    \begin{align}
        l' = l_0 \sqrt{1-v^2}
    \end{align}

@@

    And:
    \begin{align}
        e^{prst}A_{ip}A_{kr}A_{ls}A_{mt} &= -A e_{iklm} \\
        e^{iklm}e^{prst}A_{ip}A_{kr}A_{ls}A_{mt} &= 24 \;\mathrm{det}(A)
    \end{align}
    Next Landau introduces the dual tensors. Since this is important
    and the case of Lorentzian spacetime is somewhat different from
    the usual case, this topic deserves a separate treatment in the
    following section.

    \subsection{Digression: inverse of \texorpdfstring{$\Lambda$}{}}
    Here's a simple formula to get the inverse of Lorentz transformation.
    \begin{align}
        \tensor[]{(\Lambda^{-1})}{^\nu_\mu}=\tensor[]{\Lambda}{_\mu^\nu}
    \end{align}
    i.e., we drag down the first index and raise the second index, using
    of course the metric $g$.
    To put it more precise, we have:
    \begin{align}
        \Lambda\indices{^i_\sigma}\Lambda\indices{_j^\sigma}&=\delta^i_j
        \nonumber\\
        \Lambda\indices{_\sigma^i}\Lambda\indices{^\sigma_j}&=\delta^i_j
    \end{align}
    \begin{proof}
    This can be proved by noting
    $(\Lambda V, \Lambda W)=(V,W)$, i.e.
    $$
    \Lambda\indices{^\mu_\nu} V^\nu g_{\mu\mu'}
        \Lambda\indices{^{\mu'}_{\nu'}} W^{\nu'} =  
        V^\mu g_{\mu\mu'} W^{\mu'}$$
    By choosing $V$ and $W$ to have appropriate components, one can prove
    that $\Lambda\indices{^\mu_i} g_{\mu\mu'}\Lambda\indices{^{\mu'}_j}=
    g_{ij}$. Also notice that $g^2=I$. Then by multiply $g^{ik}$ to the
    left, we can get:
    \begin{align}
        g^{ik} \Lambda\indices{^\mu_k}g_{\mu\mu'}
            \Lambda\indices{^{\mu'}_j} = \delta^i_j
    \end{align}
    \end{proof}
    Actually, the above proof shows that this relation is much general,
    can be applied in all space transformations that preserve any metric.
    It only requires that the matric is idempotent.

    \subsection{Dual Tensors}
    \label{secinDual_Tensors}
    % TODO See this post:http://physics.stackexchange.com/questions/37577/what-does-the-dual-of-a-tensor-mean-e-g-dual-stress-tensor-in-relativistic-ed
    \subsection{Light's life}
    \label{sec:Lights_life}
    The life of a proton must be miserable.
